---
title: "Alcohol vs Seat choice"
author: "Ezra Licciardi"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction

We will be looking into the DavisData data set that is included with tidyverse to see if there is and correlation between alcohol consumption and the chosen seat.  

$H_0$ There is no difference in the data between alcohol and seat.

$H_A$ There is difference in the data between alcohol and seat.

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

# Meathods

Looking at the data using glimpse() we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical comparison so we will use the NumCat helper file. We will also use the mytricks to factor the categorical data useing dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova becuase we have more than two catagories and then a TukeyHSD to find where the differences are in ourt data.

# Results

## Descriptive Results

### Graphical Descriptive Results

``` {r include = TRUE, echo = FALSE}
ggplot(data = davisdata, aes(x = Seat, y = alcohol) ) +
geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
stat_boxplot (geom ='errorbar') +
labs (x = "Seat", y = "Alcohol Consumed", title = "Alcohol vs Seat Choice") +
theme (plot.title = element_text(hjust = 0.5, size = 16) )
```

We see here that the back seats dispropirtionatly consume more alcohol than the front and middle. The median of the back seats is almost at the Q4 measure in the front seats. Additionally the IQR of back seats is above the median of both the front and middle seats.

We can also see that the middle is slightly higher than the front with a higher median and has more outliers. If this were a more robust assessment we would likely see that front and middle are more similar.


### Numerical Summarys 

``` {r include = TRUE, echo = FALSE}
favstats(alcohol~Seat,data=davisdata)
```

## Inferential Tests

``` {r include = TRUE, echo = FALSE}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

```{r}
plot(TukeyHSD(model1,conf.level = 0.99))
```

## Conclusions


