---
title: "Alcohol vs Seat choice"
author: "Kiara Butler"
date: "Fall 2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
# Introduction

We will be looking into the DavisData data set that is included with tidyverse to see if there is and correlation between alcohol consumption and the chosen seat.  

$H_0$ There is no difference in the data between alcohol and seat.

$H_A$ There is difference in the data between alcohol and seat. 

```{r}
glimpse(davisdata)
davisdata <- davisdata %>%
mutate(across(where(is.character), as.factor))
```

# Methods

Looking at the data using glimpse() we can see that Alcohol is a continuous numerical and seat is a regular categorical. This problem is a numerical categorical comparison so we will use the Num~Cat helper file in CandP. We will also use the mytricks to factor the categorical data using dyplr. We will show our graphical results using ggplot2, numerical with favstats, and run inferential tests with an anova because we have more than two categories and then a TukeyHSD to find where the differences are in our data.    

# Results

## Descriptive Results

### Graphical Descriptive Results

``` {r include = TRUE, echo = FALSE}
ggplot(data = davisdata, aes(x = Seat, y = alcohol) ) +
  geom_boxplot (notch=FALSE,outlier.colour = "red",outlier.size = 2, fill = "darkgray") +
  stat_boxplot (geom ='errorbar') +
  labs (x = "Seat", y = "Alcohol Consumed", title = "Alcohol vs Seat Choice") +
  theme (plot.title = element_text(hjust = 0.5, size = 16) )
```

We see here that the back seats dispropirtionatly consume more alcohol than the front and middle. The median of the back seats is almost at the Q4 measure in the front seats. Additionally the IQR of back seats is above the median of both the front and middle seats.    

We can also see that the middle is slightly higher than the front with a higher median and has more outliers. If this were a more robust assessment we would likely see that front and middle are more similar.        


### Numerical Summaries 

``` {r include = TRUE, echo = FALSE}
favstats(alcohol~Seat,data=davisdata)
```

The median and mean of the back seats is substantially higher in the back seat class, far beyond what we would expect to see from random variations, the sample has n > 30 as well so wo would not expect large variations like what is scene here.

The $\sigma$ is also substantially larger in the back seats as well, more than double the other two categories.

## Inferential Tests

``` {r include = TRUE, echo = FALSE}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

We see here that there is a significant difference somewhere in the data, p = 0.000116 (<0.05).

```{r}
plot(TukeyHSD(model1,conf.level = 0.99))
```

We see here in the TukeyHSD the only similar categories are the Middle and Front. The back differs strongly with front and the middle and we can say with a 99% confidence that there is a correlation between Alcohol and Seat.

## Conclusions

We see here from multiple measures that the back seats disproportionately consume more alcohol than the other categories. The graphical, numerical, and inferential results show a strong difference in the data when comparing the categories. We can say that with a 99% level of confidence that there is a correlation in the data between the back seat and the other categories. We would need to review the data collection methods to ensure that this is not collected with a convenience sample that that there is no collection bias such as non-response bias. 

